Homogenization of periodic and random ferroelectric-dielectric composites

### 2019-03-26 paper/main.tex
test docker

\maketitle
\noindent values and losses.
The effective parameters of those composites have been investigated \cite{sherman_ferroelectric-dielectric_2006, jylha_tunability_2008, sherman_tunability_2004, astafiev_can_2003} and it has been found that the
permittivity can be greatly reduced while losses and tunability are much less sensitive to the
dielectric phase addition.
\\
This study investigates the effective permittivity of dielectric/ferroelectric composites
by using a two-scale convergence method \cite{allaire_homogenization_1992, guenneau_homogenization_2000}.
The originality lies in the fact that a fully coupling model is employed to
calculate the electrostatic field distribution when a uniform biasing field is
applied on the structures, which will result in a local modification of the permittivity
in the ferroelectric phase due to the microstructure. As compared to a simple uncoupled model where the
ferroelectric phase is only modified through the biasing field,
the resulting effective permittivity, dielectric losses, tunability and
anisotropy significantly differ. \\
We study first a two-dimensional model of metamaterials made of parallel rods with circular cross section,
considering both square periodic arrays and random distributions within the unit cell of
a periodic array.

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=1\textwidth]{effpar_rand_cpl}
 \caption{Effective parameters of the random 2D mixtures as a function of the
  applied electric field for various filling fraction of dielectric, when the
  coupling is taken into account.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines represent the average values
  over the 21 samples and the lighter error bands show a confidence interval corresponding to
  the standard deviation.}
 \label{eff_par_2Drand_TM}
\end{figure}
%
%
%
\begin{figure}[!t]
 \centering
 \includegraphics[width=1\textwidth]{conv_rand}
 \caption{Convergence of the coupled problem in the random case
  for one sample.
  Real part (a) and loss tangent (b) of the components of the homogenized
  permittivity tensor as a function of iteration step $i$. The distribution of
  the normalized electric field (colour map: magnitude in logarithmic scale, arrows: direction) and of the
  $xx$ component of the permittivity tensor are shown for $i=1$
  (c and d) and $i=14$ (e and f).
 }
 \label{conv_random}
\end{figure}

>>>>

\maketitle
\noindent values and losses.\\
The effective parameters of those composites have been investigated \cite{sherman_ferroelectric-dielectric_2006, jylha_tunability_2008, sherman_tunability_2004, astafiev_can_2003} and it has been found that the
permittivity can be greatly reduced while losses are much less sensitive to the dielectric phase addition, and in some can lead to a small increase of the tunability of the mixture. In the context of porous ferroelectrics, the homogenized properties strongly depends on the size and morphology of the pores \cite{okazaki_effects_1973,stanculescu_study_2015}. In addition, the influence
of local field enhancement in the tunability has been shown to be of particular importance \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012,cazacu_tunable_2013}.
\\
This study investigates the effective permittivity of composites made of dielectric inclusions in a ferroelectric matrix
by using a two-scale convergence method \cite{allaire_homogenization_1992, guenneau_homogenization_2000}.
The originality lies in the fact that a fully coupling model is employed to
calculate the electrostatic field distribution when a uniform biasing field is
applied on the structures, which will result in a local modification of the permittivity
in the ferroelectric phase due to the microstructure. As compared to a simple uncoupled model where the
ferroelectric phase is only modified through the biasing field,
the resulting effective permittivity, dielectric losses, tunability and
anisotropy significantly differ. The difference between earlier sudies in the litterature \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012} is that the non-linear coupling is taken into account beyond the first iteration and that we use two-scale
convergence homogenization theory to compute the effective parameters at higher frequencies, instead of a capacitance based model.
We study first a two-dimensional model of metamaterials made of parallel rods with circular cross section,
considering both square periodic arrays and random distributions within the unit cell of
a periodic array.

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=0.9\textwidth]{effpar_rand_cpl}
 \caption{Effective parameters of the random 2D mixtures as a function of the
  applied electric field for various filling fraction of dielectric, when the
  coupling is taken into account.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines represent the average values
  over the 21 samples and the lighter error bands show a confidence interval corresponding to
  the standard deviation.}
 \label{eff_par_2Drand_TM}
\end{figure}
%
%
%
\begin{figure}[!t]
 \centering
 \includegraphics[width=1\textwidth]{conv_rand}
 \caption{Convergence of the coupled problem in the random case
  for one sample.
  Real part (a) and loss tangent (b) of the components of the homogenized
  permittivity tensor as a function of iteration step $i$. The distribution of
  the normalized electric field (colour map: magnitude in logarithmic scale, arrows: direction) and of the
  $xx$ component of the permittivity tensor are shown for $i=1$
  (c and d) and $i=14$ (e and f).
 }
 \label{conv_random}
\end{figure}

%#########################################################################################
%
